DNA Methylation Hierarchical Variance Model\nPaper Figures

### 2021-07-30 Paper_Figures.Rmd
cardiac gene set typo fix

# stats
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="COSMIC"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="AGO"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="DEPMAP"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="neuron"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="cardprog"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
```

>>>>

# stats
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="COSMIC"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="AGO"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="DEPMAP"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="cardiac"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
wilcox.test(x = genes_dbs$score_median[genes_dbs$group=="neuron"], y = genes_dbs$score_median[genes_dbs$group=="all genes"], alternative = "greater")
```
